---
title: "Getting and Cleaning Data"
output: pdf_document
---

1.Merges the training and the test sets to create one data set.

read the test data (3 files) and merge into one test data frame (2947 obs. of 563 variables)

```{r}
subject_test <- read.table('subject_test.txt')
x_test <- read.table('X_test.txt')
y_test <- read.table('y_test.txt')
test <- cbind(subject_test,y_test,x_test)
```

read the train data (3 files) and merge into one train data frame  (7352 obs. of 563 variables)

```{r, echo=FALSE}
subject_train <- read.table('subject_train.txt')
x_train <- read.table('X_train.txt')
y_train <- read.table('y_train.txt')
train <- cbind(subject_train,y_train,x_train)
```

merge test and train data frame to create one data set (10299 obs. of 563 variables)
```{r}
dat <- rbind(test, train)
```

name dat set 'dat' each column
```{r}
feature <- read.table('features.txt')
colnames(dat)[1] <- 'SubjectId'
colnames(dat)[2] <- 'Activity'
colnames(dat)[3:563] <- as.character(feature$V2)
```

2.Extracts only the measurements on the mean and standard deviation for each measurement. Save the result to dat_short (10299 obs. of 68 variables)
```{r}
dat_short <- dat[grepl('Id', colnames(dat))|grepl('Activity', colnames(dat))|grepl('mean\\()', colnames(dat))|grepl('std\\()', colnames(dat))]
```

3.Uses descriptive activity names (read from the file "activity_labels.txt") to name the activities in the data set

```{r}
activity_label <- read.table('activity_labels.txt')
dat_short$Activity <- activity_label$V2[dat_short$Activity]
```

4.Appropriately labels the data set with descriptive variable names. Change "t" to "Time", "f" to "Freq", delete "()" , replace "-" to "."

```{r}
names(dat_short) <- sub('^t', 'Time.', sub('^f', 'Freq.',gsub('\\()', '', gsub('-', '.',names(dat_short)))))
```

5.From the data set in step 4, creates a second, independent tidy data set 
      with the average of each variable for each activity and each subject.
      Save the result to activity_clean.

```{r}
library(dplyr)
activity_clean <- dat_short %>% group_by(SubjectId,Activity) %>% summarise_each(funs(mean))
```

save the tidy data into file 'activity_clean.txt'

```{r}
write.table(activity_clean, file='activity_clean.txt', row.name=FALSE)
```
